conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-08-19 paper/paper.qmd
added a couple of small TODO notes and some small wording changes

@@

The interface to the model formula in conmat is fixed; users cannot change the covariates of the model. This means that if there is an unusual structure in their contact data it might not be accurately captured by conmat. It was a design decision that was made to focus on the key feature of conmat: using just age population data to predict a contact matrix.

>>>>

[njt: should we reference that contact patterns are known to differ?]

@@

The interface to the model formula in conmat is fixed; users cannot change the covariates of the model. This means if there is an unusual structure in their contact data it might not be accurately captured by conmat. This fixed formula was a design decision made to focus on the key feature of conmat: using just age population data to predict a contact matrix.

[njt: should we have conmat as `conmat`]
